???Grape Quality and its Link to Regional Differences in the Australian Winegrowing Industry

### 2023-08-30 article.tex
Results include figures (looking good!)

\subsection{Data}
The Australian wine industry is divided into 65 regions, known as a Geographical Indicator Regions (GI Region). Each GI Region is used to describe different unique localised traits of vineyards across Australia; with each having its own mixture of climatic and geophysical properties \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}. The climatic properties of a GI Region are summarised by Sustainable Winegrowing Australia (2021), where regions of similar climates are amalgamated together into superset regions. The climatic regions were utilised to illustrate similar trends and explain differences between sets of regions.
The data used in this analysis comes from Sustainable Winegrowing Australia and covers the period 2015 to 2022. The dataset contained 3342 samples across 52 GI Regions and 1072 individual vineyards.

% how was it collected

\subsection{XGBoosted Trees}
XGBoosted (eXtreme Gradient Boosting) trees were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. They were chosen for this analysis as they provide both a high predictive performance and ability to effectively capture complex relationships. An XGBoosted tree was created for each variable to show how they interacted. Each tree included all but the economic variables (profit and operating cost), which were only included once as predicted variables.
\par
Following Chen and Guestrin \citep{chenXGBoostScalableTree2016}, XGboosted trees predict a value $y_i$ from the input $x_i$. The method of prediction is achieved through a tree ensemble model, using $K$ additive functions to predict the output.

@@

with the tree structure is defined using left $I_L$ and right $I_R$ instance sets of nodes, with $I = I_L \cup I_R$. Instead of enumerating all possible tree structures, a greedy algorithm iteratively adds branches to the tree minimising $ \mathcal{L}_{split} $ in (\ref{eqn:enumerate}). The frequency of a variable's occurrence within a tree is directly attributed to the minimisation of the objective function (or loss) through the minimisation of  $ \mathcal{L}_{split} $.
\par
The frequency of a variable appearing as a node within the ensemble was used as a measure of importance. This measure was chosen as it connected a variable to the minimisation of its associated objective function, translating the value into a simple count metric. Creating XGBoosted trees for each variable allowed the use of importance to show how strongly variables were associated with each other. The importance of predictor variables to economic variables was illustrated through the use of Sankey diagrams constructed using the Holoviews python library \citep{philipp_rudiger_2020_3904606}. Other variable's interconnectedness was demonstrated through the use of a chord diagram also created using Holoviews.
\par
Each variable utilised 80\% of the data to train the XGBoost ensemble, with 20\% reserved for testing and validation. Testing was done through the iterative minimisation of the respective objective function for the variables type. For continuous variables 20\% was used as testing data, minimising the root-mean-square function. The final model was validated using repeated k-fold cross validation for 10 folds, repeated 10 times.
 For  binary and multiclass variables data was split into 80\% training, 10\% testing and 10\% validation data. Due to class disparity in multiclass variables (most prominently in region) data was stratified into each subset at the same ratio of class occurrence. Validation was summarised through confusion matrices and their associated accuracy 
\par
The use of the XGBoost library incorporates regularisation techniques built into the software to mitigate over-fitting and enhance model generalisation. The further use of cross validated grid search functions allowed for the selection of better performing hyperparameters when selecting the final model. The performance measure for model selection was root-mean-square error for continuous variables. The receiver operator characteristic's area under the curve was used for category variables \citep{hanley1982meaning}. Multiclass variables utilised the one verse one approach to minimise sensitivity to class disparity \citep{ferriExperimentalComparisonPerformance2009,handSimpleGeneralisationArea2001}.

@@

\subsection{Model 1 GI Regions}
The first Model was used to classify GI regions % Interestingly the firs I am hearing of this - each model needs to be more well summarised. A table would be good.
and resulted in an accuracy of 36.48\% across 52 classes. The most prominent features used to classify regions were the types of water resources available (see Figure 1). Two regions, the Riverland and Coonawarra, were the most accurate classes being 92.74\% and 96.97\% respectively.
% it might be worth only talking about the regions that were well classifified - and then talk about their determining traits.
These regions differ greatly in practice and geophysical properties, with the Riverland being a dry warm inland region and Coonawarra being a cooler, wet coastal region. However, they are both similar in operational scales, with vineyards being relatively large compared with other regions.
%Summary statistics regarding these two regions would be a better point of comparison, for example:
%
% How much in size do these operational scales differ?
% How much yield do they differ by?
% What are the differences in rainfall etc
% What makes them unique, different and similar?
%
The differences in resources and practices between these regions are also significant, such as the Riverland utilising the river Murray as a water source.
% What are the specific differences? This is a really critical part of this paper
Many of the regions had significantly lower reporting rates, resulting much poorer classification performance. % This is almost its own paragraph. Why was this case? is it important? what are the similarities and differences of regions that were poorly classified?
 The regions with the most samples performed the best (see Table 1). Notably bordering regions were routinely grouped together and misclassified as the same region, for example the two closest regions to Coonawarra, Padthaway and Wrattonbulley, were misclassified as Coonawarra even though they had 147 and 137 samples respectively. The same case was found for the Murray Darling, with 143 samples, it was misclassified as the Riverland.
 % THis speaks highly to why regions were poorly classified.
These misclassifications are likely due to the incredibly similar regional properties and close proximity these regions have with one another. Other misclassifications were most likely due to lower reporting rates with many regions being under represented.

\begin{table}[]
    \caption{Classification accuracy of the most prominent GI Regions.}
    \label{tab:accuracy}
    \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}llll@{}}
            \toprule
            \textbf{} & \textbf{Accuracy} & \textbf{Predicted} & \textbf{Actual} \\ \midrule
            \textbf{Adelaide Hills} & 30.45\% & 95 & 312 \\
            \textbf{Barossa Valley} & 51.00\% & 205 & 402 \\
            \textbf{Coonawarra} & 96.97\% & 192 & 198 \\
            \textbf{Langhorne Creek} & 22.84\% & 53 & 232 \\
            \textbf{Margaret River} & 78.82\% & 201 & 255 \\
            \textbf{McLaren Vale} & 52.89\% & 128 & 242 \\
            \textbf{Riverland} & 92.74\% & 345 &
        \end{tabular}
    }
\end{table}

>>>>

\subsection{Data}

% 6091 samples - total
% 58 regions
% 10 years

% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program, which aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by the SWA is entered manually by winegrowers using a web based interface tool. A total of 6091 observations were collected from 2012 to 2022. Each observation contained 23 variables reflecting a vineyards account for the given year (see Table \ref{tab:vars}).
\par
\begin{table}[] 
  \label{tab:vars}
  \caption{Summary of variables used in the analysis. The recorded column indicate values that were either greater than zero or that were not missing.}\label{tab:summary}
  \begin{tabular}{@{}ccccl@{}}
    \toprule
    \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ Classes\end{tabular}} &  \\ \midrule
    Water Used & Mega Litres & 5846 &  &  \\
    Diesel & Litres & 5585 &  &  \\
    Biodiesel & Litres & 25 &  &  \\
    LPG & Litres & 958 &  &  \\
    Herbicide Spray & Times per year & 2026 &  &  \\
    Year & Class & 6091 & 10 &  \\
    Disease & Class & 6091 & 2 &  \\
    Region & Class & 6091 & 58 &  \\
    Solar & Kilowatt Hours & 622 &  &  \\
    Irrigation Type & Class & 6091 & 20 &  \\
    Petrol & Litres & 4309 &  &  \\
    Slashing & Times per year & 2290 &  &  \\
    Yield & Tonnes & 5935 &  &  \\
    Irrigation Energy & Class & 6091 & 16 &  \\
    Area Harvested & Hectares & 6091 &  &  \\
    Electricity & Kilowatt Hours & 1015 &  &  \\
    Insecticide Spray & Times per year & 1092 &  &  \\
    Fertiliser & \begin{tabular}[c]{@{}c@{}}Kilograms \\ of Nitrogen\end{tabular} & 795 &  &  \\
    Fungicide Spray & Times per year & 2260 &  &  \\
    Cover Crop & Class & 6091 & 32 &  \\
    Water Type & Class & 6091 & 39 &  \\
    Profit & AUD & 853 &  &  \\
    Operating Costs & AUD & 853 &  &  \\ \bottomrule
    \end{tabular}
\end{table}

The data originally contained only two multiclass variables: year and region. Variables that measured the same metric from different sources (such as water collected from rivers versus water from dams) were converted into multiclass variables representing the source. The total amount used from these variables was retained as a separate variable. Occurrences of multiple sources were defined as separate classes. As harvest does not run by calendar year, years are in financial years. Region represents one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}. Profit was also used as a binary variable, depicting whether a vineyard was profitable or not.
\par
%
% Mention one-hot-encoding.
%

%
% How deep into the classes do we go?
%
\subsection{XGBoosted Trees}
XGBoosted (eXtreme Gradient Boosting) trees were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. They were chosen for this analysis as they provide both a high predictive performance and ability to effectively capture complex relationships. An XGBoosted tree was created for each variable to show how they interacted. Each tree included all but the economic variables (profit and operating cost), which were only included once as predicted variables.
\par
Following Chen and Guestrin \citep{chenXGBoostScalableTree2016}, XGboosted trees predict a value $y_i$ from the input $x_i$. The method of prediction is achieved through a tree ensemble model, using $K$ additive functions to predict the output.

@@

with the tree structure defined using left $I_L$ and right $I_R$ instance sets of nodes, with $I = I_L \cup I_R$. Instead of enumerating all possible tree structures, a greedy algorithm iteratively adds branches to the tree minimising $ \mathcal{L}_{split} $ in (\ref{eqn:enumerate}). The frequency of a variable's occurrence within a tree is directly attributed to the minimisation of the objective function (or loss) through the minimisation of  $ \mathcal{L}_{split} $.
\par
The frequency of a variable appearing as a node within the ensemble was used as a measure of importance. This measure was chosen as it connected a variable to the minimisation of its associated objective function, translating the value into a simple count metric. Creating XGBoosted trees for each variable allowed the use of importance to show how strongly variables were associated with each other. The importance of predictor variables to economic variables was illustrated through the use of Sankey diagrams constructed using the Holoviews python library \citep{philipp_rudiger_2020_3904606}. Other variable's interconnectedness was demonstrated through the use of a chord diagram also created using Holoviews.
\par
Each variable utilised 80\% of the data to train the XGBoost ensemble, with 20\% reserved for testing and validation. Testing was done through the iterative minimisation of the respective objective function for the variables type. For continuous variables 20\% was used as testing data, minimising the root-mean-square function. The final model was validated using repeated k-fold cross validation for 10 folds, repeated 10 times.
 For  binary and multiclass variables data was split into 80\% training, 10\% testing and 10\% validation data. Due to class disparity in multiclass variables (most prominently in region) data was stratified into each subset at the same ratio of class occurrence. Validation was summarised through confusion matrices and their associated accuracy 
\par
The use of the XGBoost library incorporates regularisation techniques built into the software to mitigate over-fitting and enhance model generalisation. The further use of cross validated grid search functions allowed for the selection of better performing hyperparameters when selecting the final model. The performance measure for model selection was root-mean-square error for continuous variables. The receiver operator characteristic's area under the curve was used for category variables \citep{hanley1982meaning}. Multiclass variables utilised the one verse one approach to minimise sensitivity to class disparity \citep{ferriExperimentalComparisonPerformance2009,handSimpleGeneralisationArea2001}.

@@

\subsection{Region}

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{region.pdf}}
  \caption{Decision tree predicting Region. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:region_tree}
\end{figure}

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{region.png}}
  \caption{The left-hand side depicts the 10 most important variables in predicting Region using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:region_sankey}
\end{figure}

\subsection{Year}

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{year.pdf}}
  \caption{Decision tree predicting Year. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:year_tree}
\end{figure}

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{year.png}}
  \caption{The left-hand side depicts the 10 most important variables in predicting Year using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:year_sankey}
\end{figure}

\subsection{Operating Costs}

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{operating_costs.pdf}}
  \caption{Decision tree predicting Operating Costs. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:operating_costs_tree}
\end{figure}

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{operating_costs.png}}
  \caption{The left-hand side depicts the 10 most important variables in predicting Operating Costs using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:operating_costs_sankey}
\end{figure}

\subsection{Profit}

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{profit.pdf}}
  \caption{Decision tree predicting Profit. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:profit_tree}
\end{figure}

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{profit.png}}
  \caption{The left-hand side depicts the 10 most important variables in predicting Profit using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:profit_sankey}
\end{figure}

\subsection{Validation}

\begin{table}[]
  \caption{Validation and training accuracies of each multiclass variable.}
  \begin{tabular}{@{}ccc@{}}
  \toprule
  \textbf{Variable} & \textbf{Validation} & \textbf{Training} \\ \midrule
  \textbf{cover crops} & 0.364086 & 0.396418 \\
  \textbf{water type} & 0.742097 & 0.928905 \\
  \textbf{profitable} & 0.705882 & 0.719737 \\
  \textbf{irrigation type} & 0.841845 & 0.847554 \\
  \textbf{giregion} & 0.505824 & 0.568242 \\
  \textbf{irrigation energy} & 0.746293 & 0.836405 \\
  \textbf{data year id} & 0.422003 & 0.518059 \\ \bottomrule
  \end{tabular}
  \end{table}

\subsection{Model 1 GI Regions}

The first Model was used to classify GI regions % Interestingly the firs I am hearing of this - each model needs to be more well summarised. A table would be good.
and resulted in an accuracy of 36.48\% across 52 classes. The most prominent features used to classify regions were the types of water resources available (see Figure 1). Two regions, the Riverland and Coonawarra, were the most accurate classes being 92.74\% and 96.97\% respectively.
% it might be worth only talking about the regions that were well classifified - and then talk about their determining traits.
These regions differ greatly in practice and geophysical properties, with the Riverland being a dry warm inland region and Coonawarra being a cooler, wet coastal region. However, they are both similar in operational scales, with vineyards being relatively large compared with other regions.
%Summary statistics regarding these two regions would be a better point of comparison, for example:
%
% How much in size do these operational scales differ?
% How much yield do they differ by?
% What are the differences in rainfall etc
% What makes them unique, different and similar?
%
The differences in resources and practices between these regions are also significant, such as the Riverland utilising the river Murray as a water source.
% What are the specific differences? This is a really critical part of this paper
Many of the regions had significantly lower reporting rates, resulting much poorer classification performance. % This is almost its own paragraph. Why was this case? is it important? what are the similarities and differences of regions that were poorly classified?
 The regions with the most samples performed the best (see Table 1). Notably bordering regions were routinely grouped together and misclassified as the same region, for example the two closest regions to Coonawarra, Padthaway and Wrattonbulley, were misclassified as Coonawarra even though they had 147 and 137 samples respectively. The same case was found for the Murray Darling, with 143 samples, it was misclassified as the Riverland.
 % THis speaks highly to why regions were poorly classified.
These misclassifications are likely due to the incredibly similar regional properties and close proximity these regions have with one another. Other misclassifications were most likely due to lower reporting rates with many regions being under represented.

% \begin{table}[]
%     \caption{Classification accuracy of the most prominent GI Regions.}
%     \label{tab:accuracy}
%     \resizebox{\textwidth}{!}{
%         \begin{tabular}{@{}llll@{}}
%             \toprule
%             \textbf{} & \textbf{Accuracy} & \textbf{Predicted} & \textbf{Actual} \\ \midrule
%             \textbf{Adelaide Hills} & 30.45\% & 95 & 312 \\
%             \textbf{Barossa Valley} & 51.00\% & 205 & 402 \\
%             \textbf{Coonawarra} & 96.97\% & 192 & 198 \\
%             \textbf{Langhorne Creek} & 22.84\% & 53 & 232 \\
%             \textbf{Margaret River} & 78.82\% & 201 & 255 \\
%             \textbf{McLaren Vale} & 52.89\% & 128 & 242 \\
%             \textbf{Riverland} & 92.74\% & 345 &
%         \end{tabular}
%     }
% \end{table}
